Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-06-25 paper.qmd
Added MNIST scripts

```{r}
#| label: combine-data-mnist

@@

<!-- Fit the model and compute error-->
```{r}
#| label: hexbin-mnist

@@

```{r}
#| label: img-diff-pos

>>>>

<!--mnist/6_gen_mse_for_diff_methods.R-->
```{r}
#| label: combine-data-mnist

@@

<!-- Fit the model and compute error-->
<!--mnist/9_gen_model_with_tSNE.R-->
```{r}
#| label: hexbin-mnist

@@

<!--mnist/5_gen_images.R-->
```{r}
#| label: img-diff-pos
